---
title: "Simple document"
output: github_document
---

```{r}
library(tidyverse)
library(readxl)
library(haven)
```

Let's import the 'FAS_litters.csv' csv using a relative path

```{r}
litters_df =
  read_csv("Data/FAS_litters.csv")

#Cleaning the column names and standardizing organization
litters_df =
  janitor::clean_names(litters_df)

litters_df

```

Import the dataset using an absolute path. But relative paths are much stronger because they do not change if the files are moved around on your computer.

```{r, eval = FALSE}
litters_df_abs =
  read_csv("~/Desktop/GitHub Example/Data Wrangling Lesson/Data/FAS_litters.csv")

#Cleaning the column names and standardizing organization
litters_df_abs =
  janitor::clean_names(litters_df_abs)

litters_df_abs

```

Learning Assessment 

```{r}
pups_df =
  read_csv("Data/FAS_pups.csv")

pups_df =
  janitor::clean_names(pups_df)

pups_df
```

## Looking at data

```{r}
litters_df

#These functions bring you to the top and bottom of a dataframe 
head(litters_df)
tail(litters_df)

```

You can use 'View' for the entire dataset. Better to use separately in a consoline line command and not knit into an R Markdown file 

```{r, eval = FALSE}
view(litters_df)

```

Look at a Data Summary

```{r}
str(litters_df)

skimr::skim(litters_df)

```

## Options in 'Read_*'

```{r}
litters_df_skipped =
  read_csv("Data/FAS_litters.csv",
           skip = 10, col_names = FALSE)
```

Looking at NA Values

```{r}
litters_df =
  read_csv("Data/FAS_litters.csv",
           na = c("NA", 19))
```

Column Types

```{r}
litters_df = 
  read_csv("Data/FAS_Litters.csv",
           col_types = 
             cols(
               `GD0 weight` = col_character()
             ))
litters_df
```

#Other File Types

Importing a xlsx file first

```{r}
mlb_df =
  read_excel("Data/mlb11.xlsx")
mlb_df
```

Importing a SAS File

```{r}
pulse_df = 
  read_sas("Data/public_pulse_data.sas7bdat")

```

